---
title: "msdata2 package"
author: "Chong Tang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{msdata2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Introduction
The `msdata2` package mainly contains a set of public accessible label-free Proteomics datasets. The purpose of this data package is to provide cleaned, formatted, compressed and extensible proteomics datasets to the research community.  
Moreover, this package will also be built as a benchmarking data repository, which provides standard and curated datasets to facilitate the benchmarking of different quanfitication workflows.

# Datasets
The package contains the following datasets:  
    I. Raw MS datasets:  
    
    II. Expression datasets:
        -  DIA/SWATH-MS:
            * SWATH-MS Gold Standard Dataset
            * OpenSWATH Spyogenes Dataset
        -  Label-free quantification:
            *  Yeast + UPS1 spiked datasets X8

# Handling Expression data

# Importing data
## Load data
## Exploring the data

# Contribution guidelines

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(msdata2)
```
